---
params:
   md_lang: "ru"
title: "`r switch(params$md_lang,ru='Живая природа Арктики','Wildlife of the Arctic')`"
pagetitle: "`r switch(params$md_lang,ru='Живая природа Арктики','Wildlife of the Arctic')`"
output:
  html_document:
    output_dir: sss
---

```{r, echo=FALSE, include=FALSE}
if (!exists("md_lang"))
   md_lang <- params$md_lang #"ru"
md_altlang <- switch(md_lang,ru="en",en="ru")
Sys.setlocale("LC_CTYPE",switch(md_lang,ru="Russian","Russian"))
Sys.setlocale("LC_TIME",switch(md_lang,ru="Russian","English"))
md_title <- switch(md_lang,ru="Живая природа Арктики","Wildlife of the Arctic")
md_subtitle <- switch(md_lang,ru="Дополнения к официальному сайту","Supplemental information")
md_author <- switch(md_lang,ru="","")
md_date <- switch(md_lang,ru="Обновлено:","Updated:")
md_index <- switch(md_lang,ru="Преамбула","Preface")
md_schedule <- switch(md_lang,ru="Программа","Program")
md_speakers <- switch(md_lang,ru="Докладчики","Speakers")
md_roundtable <- switch(md_lang,ru="Круглые столы","Round tables")
md_location <- switch(md_lang,ru="Местоположение","Location")
md_abstract <- switch(md_lang,ru="Аннотации","Abstracts")
md_yourlanguage <- switch(md_lang,ru="In English | по-русски","По-русски | In English")
md_switchlanguage <- switch(md_lang,ru="In English","По-русски")
md_subject <- switch(md_lang,ru="Тематика","Subjects")
md_photo <- switch(md_lang,ru="Фотогалерея","Photos")
md_resolution  <- switch(md_lang,ru="Резолюция","Conclusion")
output <- rmarkdown::all_output_formats(knitr::current_input())[1]
isPDF <- length(grep("pdf",output))>0
isHTML <- length(grep("html|github",output))>0
isBOOK <- length(grep("book",output))>0
if (!isBOOK & !isPDF & !isHTML)
   isHTML <- TRUE
options(md_lang=md_lang,md_isHTML=isHTML)
```

---
date: "`r paste(md_date,format(Sys.time(),'%Y-%m-%d %H:%M'))`"
documentclass: book
biblio-style: apalike
link-citations: yes
description: "Everything you need (and nothing more) to start a bookdown book."
output_dir: "qqqrrr"
favicon: aes2017.gif

---


# `r md_index` {- #index_`r md_lang`}
<!--  # <span style="font-size:60%">`r md_index`</span> {- #index_`r md_lang`} -->

```{r preface, child=paste0("about-",md_lang,".Rmd"),eval=TRUE}
```

# `r md_subject` {- #subject_`r md_lang`}

```{r subject, results='asis', echo=FALSE, eval=TRUE}
source("subject.R",encoding="utf8")
```

# `r md_schedule` {- #schedule_`r md_lang`}

```{r schedule,echo=FALSE, results='asis', eval=TRUE}
source("schedule.R",encoding="utf8")
```

<!---->
# `r md_speakers` {- #speakers_`r md_lang`}
<!---->

```{r speakers,echo=FALSE, results='asis', eval=TRUE}
source("speakers.R",encoding="utf8")
```
<!---->
# `r md_location` {- #location_`r md_lang`}
<!---->

```{r leafletPrepare, include=FALSE, eval=TRUE}
source("location.R",encoding="utf8")
```
```{r leafletShow,echo=FALSE, eval=TRUE}
m
```

<!---->
# `r md_abstract` {- #abstract_`r md_lang`}
<!---->

```{r abstract, results='asis', echo=FALSE, eval=TRUE}
source("abstract.R",encoding="utf8")
```

# `r md_resolution` {- #resolution_`r md_lang`}

Текст резолюции в настоящее время формируется оргкомитетом.

Conference conclusion will be available in Russian soon.

# `r md_photo` {- #photo_`r md_lang`}

```{r photo, child="photo.Rmd",eval=TRUE}
```

<!--
# <span style="font-size:100%">`r md_yourlanguage`</span> {- #index}

[Русский](index-ru.html)
[English](index-en.html)
Suomalainen
-->

# [`r md_switchlanguage`](index-`r md_altlang`.html) {- #switch-`r md_lang`}
